# The Effects of Measurement Error

We will look into effects of ME in the linear regression case.

## Classical Measurement Error

 
```{r, echo=FALSE,  screenshot.opts = list(delay = 10)}
knitr::include_url("https://stefaniemuff.shinyapps.io/MEC_ChooseL/",height = "600px")
```


## The Concept of Heritability, Regression to the Mean and Measurement Error  {#sec:heritability}

Geneticists, evolutionary biologists and animal breeders will be familiar with the concept of *heritability* \@ref(eq:heritability).


\begin{equation}
h^2 = \frac{\sigma_A^2}{\sigma_A^2 + \sigma_E^2}
(\#eq:heritability)
\end{equation}

- Will use data in Figures \@ref(fig:galton1) and \@ref(fig:galton2) to explain regression to the mean

```{r galton1, echo=F, fig=T,fig.width=5,fig.height=5,fig.align="center",fig.cap="Data drawn from `http://www.math.uah.edu/stat/data/Galton.txt`"}
galton <- read.table("data/Galton.txt",header=T)
galton$midparent <- 0.5 * (galton$Father + galton$Mother)
r.lm <- lm(Height ~ midparent,data=galton)
plot(Height ~ midparent,galton,xlab="Mid parents height",ylab="Offspring height",xlim=c(60,74))
abline(c(0,1),col=2,lwd=2)
abline(r.lm)
```

```{r galton2, echo=F, fig=T,fig.width=5,fig.height=5,fig.align="center",fig.cap="Data drawn from `http://www.math.uah.edu/stat/data/Galton.txt`"}
galton <- read.table("data/Galton.txt",header=T)
galton$midparent <- 0.5 * (galton$Father + galton$Mother)
r.lm2 <- lm(midparent ~ Height,data=galton)
plot(midparent ~ Height,galton,xlab="Offspring height",ylab="Mid parents height",xlim=c(60,74))
abline(c(0,1),col=2,lwd=2)
abline(r.lm2)
```

[@fuller1987;@galton1886]


## Berkson Measurement Error

```{r, echo=FALSE,  screenshot.opts = list(delay = 10)}
knitr::include_url("https://stefaniemuff.shinyapps.io/MEB_ChooseL/",height = "600px")
```


## Error in Categorical and Count Variables



## Error in the response

